Midterm - Predicting Housing Prices

### 2023-07-04 Draft_Mid_Term_test.Rmd

```{r spatial lag}

coords <- st_coordinates(data) 
neighborList <- knn2nb(knearneigh(coords, 5))

spatialWeights <- nb2listw(neighborList, style="W")

data$lagPrice <- lag.listw(spatialWeights, data$price)
```

@@

stargazer(M2, type = "html", 
          title = "Table 4.1.3 Summary Statistics of Model.2 ",
          header = FALSE,
          single.row = TRUE)
```

@@

```{r results='asis',warning=FALSE,message=FALSE}
train_set.2<-model_set.train %>%
  dplyr::select(
  price,
  #Non-numeric Feature
  bldggrade.m,
  #Internal Feature
  shape_Area ,heatedarea,fullbaths,bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite,MedHHInc,test.elementary,crime_sum,PctLongCommute,Pctgrocery,isin,lagPrice,
  #Amenities Feature
  college_nn5,library_nn2,hist_properties_nn5,capital_improve_nn2
 ) %>% st_drop_geometry()

>>>>

@@

@@

```{r results='asis',warning=FALSE,message=FALSE}
train_set.2<-model_set.train %>%
  dplyr::select(
  price,
  #Non-numeric Feature
  bldggrade.m,
  #Internal Feature
  shape_Area ,heatedarea,fullbaths,bedrooms , units,
  #Tract Feature
  pctRenterOccupied , pctWhite,MedHHInc,test.elementary,crime_sum,PctLongCommute,Pctgrocery,isin,
  #Amenities Feature
  college_nn5,library_nn2,hist_properties_nn5,capital_improve_nn2
 ) %>% st_drop_geometry()
